HTW Data Dictionary

### 2023-08-08 Analysis/data_dictionary.qmd
sync updates and bayes learn models

@@

id - unique subject identifier 
condit - primary training manipulation, Constant vs. Varied. 
tOrder - whether testing phase starts with extrapolation testing
expMode2

>>>>

### Trial-level data - variables
id - unique subject identifier 
condit - primary training manipulation, Constant vs. Varied. 
tOrder - order of blocks in no-feedback testing stage (extrapolation first or re-do train first)
expMode2 - Phase of Experiment - Train, Train-Nf, Test, Test-Fb
gt.train - training trial number - running total 
vb - velocity band on current trial - Levels: 100-300 350-550 600-800 800-1000 1000-1200 1200-1400
bandInt - numeric value of lower bound of vb: 100, 350, 600, 800, 1000, 1200
vx - X velocity generated by subject on current trial 
dist - absolute distance from edge of target velocity band (0 if vx falls within band)
sdist - signed distance from edge of target velocity band
vy - y velocity generated by subject (not relevant to task)
result - categorical result of throw in relation to target band - Levels: Over, Under, Hit
vxCat - which velocity band the current trial throw falls into
prev - Target velocity band on previous throw
bandSeq - Previous Target Band and current Target Band, e.g. 800->1000  1000->1200 etc.

@@
